Research paper

### 2012-12-20 Research paper.tex
RTP: fixed typos, RP: deleted comments
RP: worked on indentifying skipgrams techniques and mbt with free word orders

% Constraint Satisfaction Inference

@@

% Drie vormen freq: raw frequency, context frequency, multilingual alignmetn

@@

\subsubsection{Identifying and extracting constructions in a language}
When using large corpora, the process of discovering simple n-grams might already take quite a lot of time; adding variability in lenght and one or multiple gaps to the n-grams makes the process even more - in fact, many times more - complex. However, as I write this, this problem has been solved by using two techniques: (1) by optimizing how the various tokens and the n-grams and skipgrams they are part of are saved in memory, and (2) by using an iterative counting algorithm to limit storage. Besides identifying the constructions, various frequency statistics can be given. These frequencies can then be used to create graphs which display the relations between the various constructions.

%Hoe is dit probleem precies opgelost?

@@

\subsubsection{It is unclear how well the memory-based approach works for non-European languages}

Memory-based learning generated a translation on the basis of context. This works well for languages in which word order is largely fixed, like English: for these languages, if you change the position of a particular word in the sentence (and thus the context), you also change the meaning of that sentence. There are languages, however, with relatively free word order; so a word can have roughly the same meaning on various places in the sentence, and thus with various contexts. In other words, in these languages the main source of the knowledge of memory-based learning isn't fully available.

% Uitzoeken

>>>>

@@

@@

\subsubsection{Identifying and extracting constructions in a language}
When using large corpora, the process of discovering simple n-grams might already take quite a lot of time; adding variability in lenght and one or multiple gaps to the n-grams makes the process even more - in fact, many times more - complex. To techniques are used to reduce the processing load:

\begin{itemize}
\item Optimization of how the various the n-grams and skipgrams are saved in memory. By reserving the labels that don't take a lot of memory for the most frequent grams, a lot of memory can be saved.
\item For trigrams and larger, taking into account the frequencies of the parts (in case of a trigram, two two-grams). If these parts do not exist or are very infrequent, there is no use in looking for the whole - if even the parts don't exist, the whole won't exist for sure.
\end{itemize}

@@

\subsubsection{It is unclear how well the memory-based approach works for languages with a more free word order}

Memory-based learning generated a translation on the basis of context. This works well for languages in which word order is largely fixed, like English: for these languages, if you change the position of a particular word in the sentence (and thus the context), you also change the meaning of that sentence. There are languages, however, with relatively free word order; Hungarian, Russian and Finish, to name a few. In these languages, changing the position and thus the context of a particular word or phrase doesn't (really) change the meaning of the sentence. In other words, in these languages the main source of the knowledge of memory-based learning isn't fully available, which may very well mean that memory-based translation may not be useful for these languages. To what extent this really is the case is completely unclear. \\\indent
